---
title: "EDA"
author: "Sriram Namana"
date: "29/09/2021"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
library(ggpubr)
library(lubridate)
library(stringr)
library(tidyr)
library(zoo)
library(thematic)
library("viridis")
```
Set plot theme
```{r}
thematic_on()
```



```{r}
wo = read.csv("wo_fans.csv")
with = read.csv("with_fans.csv")
wo$fans_present = 'N'
with$fans_present = 'Y'
head(wo)
head(with)
```



Finding points won by home and away teams with fans
```{r}
with <- with %>% 
  mutate(home_points_won = ifelse(home_ft_score > away_ft_score, 3, ifelse(home_ft_score == away_ft_score, 1, 0)),
         away_points_won = ifelse(away_ft_score > home_ft_score, 3, ifelse(away_ft_score == home_ft_score, 1, 0)),
         home_result = ifelse(home_ft_score > away_ft_score, 'W', ifelse(home_ft_score == away_ft_score, 'D', 'L')),
         away_result = ifelse(away_ft_score > home_ft_score, 'W', ifelse(away_ft_score == home_ft_score, 'D', 'L')))
with
```

Finding points won by home and away teams without fans
```{r}
wo <- wo %>% 
  mutate(home_points_won = ifelse(home_ft_score > away_ft_score, 3, ifelse(home_ft_score == away_ft_score, 1, 0)),
         away_points_won = ifelse(away_ft_score > home_ft_score, 3, ifelse(away_ft_score == home_ft_score, 1, 0)),
         home_result = ifelse(home_ft_score > away_ft_score, 'W', ifelse(home_ft_score == away_ft_score, 'D', 'L')),
         away_result = ifelse(away_ft_score > home_ft_score, 'W', ifelse(away_ft_score == home_ft_score, 'D', 'L')))
wo
```

```{r}
both_seasons = rbind(with,wo)
both_seasons
```

Plot 1: Results
```{r}
ggplot(both_seasons, mapping = aes(x=home_result, fill = fans_present)) + geom_histogram(stat = "count", position = "dodge") + labs(x = " Home result", y = "Count", title = "Home result comparison", fill = "Presence of Fans")+  scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```


```{r}
home_avg_shots_on_target =  both_seasons %>%
                              group_by(home_team, fans_present) %>%
                              summarize(home_shots_on_target = mean(home_shots_on_target))

away_avg_shots_on_target =  both_seasons %>%
                              group_by(home_team, fans_present) %>%
                              summarize(away_shots_on_target = mean(away_shots_on_target))
home_avg_shots_on_target
away_avg_shots_on_target
```

Overall average shots on target
```{r}
overall_home_avg_sot = home_avg_shots_on_target %>%
                            group_by(fans_present)%>%
                            summarize(overall_home_sot = mean(home_shots_on_target))
overall_home_avg_sot


overall_away_avg_sot = away_avg_shots_on_target %>%
                            group_by(fans_present)%>%
                            summarize(overall_away_sot = mean(away_shots_on_target))
overall_away_avg_sot
```

Plot 2a: Home shots on Target
```{r}
ggplot(home_avg_shots_on_target, mapping = aes(x=home_team, y = home_shots_on_target, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = " Home Team", y = "Shots on Target", title = "Home Shots on Target comparison", fill = "Presence of Fans") + scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 2b: Away Shots on Target
```{r}
ggplot(away_avg_shots_on_target, mapping = aes(x=home_team, y = away_shots_on_target, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))+ labs(x = " Home Team", y = "Shots on Target", title = "Away Teams Shots on Target comparison ", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 2c: Overall home shots on target
```{r}
ggplot(overall_home_avg_sot, mapping = aes(x=fans_present, y = overall_home_sot)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Presence of fans", y = "Overall Shots on Target", title = "Shots on Target comparison with and without fans for Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 2d: Overall away shots on target
```{r}
ggplot(overall_away_avg_sot, mapping = aes(x=fans_present, y = overall_away_sot)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Presence of fans", y = "Overall Shots on Target", title = "Shots on Target comparison with and without fans for Away Teams", fill = "Presence of Fans")
```


```{r}
home_avg_shots =  both_seasons %>%
                              group_by(home_team, fans_present) %>%
                              summarize(home_shots = mean(home_shots))

away_avg_shots =  both_seasons %>%
                              group_by(home_team, fans_present) %>%
                              summarize(away_shots = mean(away_shots))
home_avg_shots
away_avg_shots
```


```{r}
overall_home_avg_shots = home_avg_shots %>%
                            group_by(fans_present)%>%
                            summarize(overall_home_shots = mean(home_shots))
overall_home_avg_shots


overall_away_avg_shots = away_avg_shots %>%
                            group_by(fans_present)%>%
                            summarize(overall_away_shots = mean(away_shots))
overall_away_avg_shots
```

Plot 3a: Home shots
```{r}
ggplot(home_avg_shots, mapping = aes(x=home_team, y = home_shots, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "No. of Shots Taken", title = "Shots taken by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 3b: Away shots
```{r}
ggplot(away_avg_shots, mapping = aes(x=home_team, y = away_shots, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "No. of Shots Taken", title = "Shots taken by Away Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 3c: Overall home shots
```{r}
ggplot(overall_home_avg_shots, mapping = aes(x=fans_present, y = overall_home_shots)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall No. of Shots Taken", title = "Overall Shots taken by Home Teams", fill = "Presence of Fans")
```

Plot 3d: Overall away shots
```{r}
ggplot(overall_away_avg_shots, mapping = aes(x=fans_present, y = overall_away_shots)) + geom_bar(stat = "identity" , fill = c("#ff6961", "#78c5dc"),width = 0.30)+ labs(x = "Fans Presence", y = "Overall No. of Shots Taken", title = "Overall Shots taken by Away Teams", fill = "Presence of Fans")
```


```{r}
team_avg_possession = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_possession = mean(home_possession))
team_avg_possession

overall_possession = team_avg_possession %>%
                        group_by(fans_present) %>%
                        summarize(possession = mean(avg_possession))
overall_possession
```

Plot 4a: Possession
```{r}
ggplot(team_avg_possession, mapping = aes(x=home_team, y = avg_possession, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))+ labs(x = "Team Name", y = "Average posession", title = "Average posession by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))

```

Plot 4b: Overall possession
```{r}
ggplot(overall_possession, mapping = aes(x=fans_present, y = possession)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"), width = 0.30)+ labs(x = "Fans Presence", y = "Overall Possesion", title = "Overall Posession of Home Teams", fill = "Presence of Fans")
```


```{r}
home_yellow_cards = both_seasons %>%
                      group_by(home_team, fans_present) %>%
                      summarize(home_avg_yellow_cards = mean(home_yellow_cards))
away_yellow_cards = both_seasons %>%
                      group_by(home_team, fans_present) %>%
                      summarize(away_avg_yellow_cards = mean(away_yellow_cards))

home_yellow_cards
away_yellow_cards
```

```{r}
overall_home_yc = home_yellow_cards %>%
                    group_by(fans_present) %>%
                    summarize(home_yc = mean(home_avg_yellow_cards))

overall_away_yc = away_yellow_cards %>%
                    group_by(fans_present) %>%
                    summarize(away_yc = mean(away_avg_yellow_cards))

overall_home_yc
overall_away_yc
```

Plot 5a: Home yellow cards
```{r}
ggplot(home_yellow_cards, mapping = aes(x=home_team, y = home_avg_yellow_cards, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))+ labs(x = "Team Name", y = "Average Yellow Cards", title = "Average No. of Yellow Cards by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 5b: Away yellow cards
```{r}
ggplot(away_yellow_cards, mapping = aes(x=home_team, y = away_avg_yellow_cards, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Average Yellow Cards", title = "Average No. of Yellow Cards by Away Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 5c: Overall home yellow cards
```{r}
ggplot(overall_home_yc, mapping = aes(x=fans_present, y = home_yc)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"), width = 0.30) + labs(x = "Fans Presence", y = "Overall Average of yellow cards", title = "Overall Average of Yellow Cards for Home Teams", fill = "Presence of Fans")
```

Plot 5d: Overall away yellow cards
```{r}
ggplot(overall_away_yc, mapping = aes(x=fans_present, y = away_yc)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall Average Yellow Cards", title = "Overall Average No. of Yelllow cards for Away Teams", fill = "Presence of Fans")
```

Fouls conceded 
```{r}
home_fouls = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_home_fouls_conceded = mean(home_fouls_conceded))
away_fouls = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_away_fouls_conceded = mean(away_fouls_conceded))
home_fouls
away_fouls
```

```{r}
overall_home_fouls = home_fouls %>%
                        group_by(fans_present) %>%
                        summarize(overall_hf = mean(avg_home_fouls_conceded))
overall_away_fouls = away_fouls %>%
                        group_by(fans_present) %>%
                        summarize(overall_af = mean(avg_away_fouls_conceded))
overall_home_fouls
overall_away_fouls
```


Plot 6a: Home fouls conceded
```{r}
ggplot(home_fouls, mapping = aes(x=home_team, y = avg_home_fouls_conceded, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) +labs(x = "Team Name", y = "Fouls Conceded", title = "No. of fouls conceded by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 6b: Away fouls conceded 
```{r}
ggplot(away_fouls, mapping = aes(x=home_team, y = avg_away_fouls_conceded, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))+ labs(x = "Team Name", y = "Fouls Conceded", title = "No. of fouls conceded by Away Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 6c: Overall home fouls conceded
```{r}
ggplot(overall_home_fouls, mapping = aes(x=fans_present, y = overall_hf)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall FOuls conceded", title = "Overall Fouls conceded for Home Teams", fill = "Presence of Fans")
```

Plot 6d: Overall away fouls conceded
```{r}
ggplot(overall_away_fouls, mapping = aes(x=fans_present, y = overall_af)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall Fans Conceded", title = "Overall fouls conceded for Away Teams", fill = "Presence of Fans")
```

```{r}
home_goals_scored = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_goals_scored = mean(home_ft_score))
home_goals_scored
```

```{r}
home_goals_scored_avg = home_goals_scored %>%
                        group_by(fans_present) %>%
                        summarize(net_avg_goals = mean(avg_goals_scored))

home_goals_scored_avg
```

Plot 7a: Home goals scored  team-wise 
```{r}
ggplot(home_goals_scored, mapping = aes(x=home_team, y = avg_goals_scored, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Average Goals Scored", title = "Average No. of goals scored by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))

```

Plot 7b: Net Home goals with and without fans
```{r}
ggplot(home_goals_scored_avg, mapping = aes(x=fans_present, y = net_avg_goals)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = " Net Home Goals", title = "Net Home goals", fill = "Presence of Fans")
```



```{r}
home_goals_conceded = both_seasons %>%
                            group_by(home_team, fans_present) %>%
                            summarize(avg_goals_conceded = mean(away_ft_score))
home_goals_conceded
```

```{r}
home_goals_conceded_avg = home_goals_conceded %>%
                            group_by(fans_present) %>%
                            summarize(net_avg_goals = mean(avg_goals_conceded))

home_goals_conceded_avg
```


Plot 8a: Home goals conceded
```{r}
ggplot(home_goals_conceded, mapping = aes(x=home_team, y = avg_goals_conceded, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Average Goals Conceded", title = "Goals conceded by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))

```

Plot 8b: Net Home goals conceded with and without fans
```{r}
ggplot(home_goals_conceded_avg, mapping = aes(x=fans_present, y = net_avg_goals)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Average goals conceded", title = "Net Average Goals Conceded for Home Teams", fill = "Presence of Fans")
```


Plot 9: Minutes of goals scored
```{r}
thematic_on()
home_goal_minutes_fans <- as.numeric(na.omit(unlist(strsplit(with$home_goals_mins, ','))))
away_goal_minutes_fans <- as.numeric(na.omit(unlist(strsplit(with$away_goals_mins, ','))))
home_goal_minutes_no_fans <- as.numeric(na.omit(unlist(strsplit(wo$home_goals_mins, ','))))
away_goal_minutes_no_fans <- as.numeric(na.omit(unlist(strsplit(wo$away_goals_mins, ','))))
hgf <- gghistogram(home_goal_minutes_fans, bins = 18, color = 'darkgreen', fill = 'darkgreen', xlab = 'Minute', ylab = 'Goals', title = 'Home goals with fans')
hgnf <- gghistogram(home_goal_minutes_no_fans, bins = 18, color = 'darkgreen', fill = 'darkgreen', xlab = 'Minute', ylab = 'Goals', title = 'Home goals without fans')
agf <- gghistogram(away_goal_minutes_fans, bins = 18, color = 'red', fill = 'red', xlab = 'Minute', ylab = 'Goals', title = 'Away goals with fans')
agnf <- gghistogram(away_goal_minutes_no_fans, bins = 18, color = 'red', fill = 'red', xlab = 'Minute', ylab = 'Goals', title = 'Away goals without fans')
ggarrange(hgf, agf, hgnf, agnf,
          nrow = 2,
          ncol = 2)
```


```{r}
calculate_points_lp = function(home_mins, away_mins, home_points)
{
  if(as.integer(home_points) == 0)
  {
    return(as.integer(0))
  }
  else if(is.na(home_mins) && is.na(away_mins))
  {
    return(as.integer(0))
  }
  else
  {
      home_mins = str_replace_all(home_mins, "[[:punct:]]", "")
      h_minutes = as.integer(unlist(strsplit(home_mins, ' ')))
      away_mins = str_replace_all(away_mins, "[[:punct:]]", "")
      a_minutes = as.integer(unlist(strsplit(away_mins, ' ')))
      i = 1
      j = 1
      h_goals = 0
      a_goals = 0
      while(i <= length(h_minutes) && j <= length(a_minutes))
      {
        if(h_minutes[i] == a_minutes[j])
        {
          i = i+1
          h_goals = h_goals + 1
          j = j+1
          a_goals = a_goals + 1
        }
        else if(h_minutes[i] < a_minutes[j])
        {
          i = i+1
          h_goals = h_goals+1
        }
        else
        {
          j = j+1
          a_goals = a_goals+1
        }
        if(a_goals>h_goals)
        {
          return(as.integer(home_points))
        }
      }
      return(as.integer(0))
  }
}

for(i in 1:437)
{
  both_seasons$home_points_from_lp[i] = calculate_points_lp(both_seasons$home_goals_mins[i], both_seasons$away_goals_mins[i], both_seasons$home_points_won[i])
}
both_seasons
```


```{r}
home_losing_points = both_seasons %>%
                      group_by(home_team, fans_present) %>%
                      summarize(home_avg_losing_points = mean(home_points_from_lp))

home_losing_points
```


```{r}
overall_home_lp = home_losing_points %>%
                              group_by(fans_present) %>%
                              summarize(lp = mean(home_avg_losing_points))
overall_home_lp
```


Plot 10a: Teamwise average points won from losing positions
```{r}
ggplot(home_losing_points, mapping = aes(x=home_team, y = home_avg_losing_points, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Average Points won from losing positions", title = "Average Points won from losing positions by Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))

```


Plot 10b: Overall average points won from losing positions
```{r}
ggplot(overall_home_lp, mapping = aes(x=fans_present, y = lp)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall Points won from losing positions", title = "Overall Average of points won from losing positions for Home Teams", fill = "Presence of Fans")
```

```{r}
calculate_points_wp = function(home_mins, away_mins, home_points)
{
  if(as.integer(home_points) == 3)
  {
    return(as.integer(0))
  }
  else if(is.na(home_mins) && is.na(away_mins))
  {
    return(as.integer(0))
  }
  else
  {
      home_mins = str_replace_all(home_mins, "[[:punct:]]", "")
      h_minutes = as.integer(unlist(strsplit(home_mins, ' ')))
      away_mins = str_replace_all(away_mins, "[[:punct:]]", "")
      a_minutes = as.integer(unlist(strsplit(away_mins, ' ')))
      i = 1
      j = 1
      h_goals = 0
      a_goals = 0
      while(i <= length(h_minutes) && j <= length(a_minutes))
      {
        if(h_minutes[i] == a_minutes[j])
        {
          i = i+1
          h_goals = h_goals + 1
          j = j+1
          a_goals = a_goals + 1
        }
        else if(h_minutes[i] < a_minutes[j])
        {
          i = i+1
          h_goals = h_goals+1
        }
        else
        {
          j = j+1
          a_goals = a_goals+1
        }
        if(h_goals>a_goals)
        {
          return(as.integer(3 - home_points))
        }
      }
      return(as.integer(0))
  }
}

for(i in 1:437)
{
  both_seasons$home_points_from_wp[i] = calculate_points_wp(both_seasons$home_goals_mins[i], both_seasons$away_goals_mins[i], both_seasons$home_points_won[i])
}
both_seasons
```

```{r}
home_winning_points = both_seasons %>%
                      group_by(home_team, fans_present) %>%
                      summarize(home_avg_winning_points = mean(home_points_from_wp))

home_winning_points
```


```{r}
overall_home_wp = home_winning_points %>%
                              group_by(fans_present) %>%
                              summarize(wp = mean(home_avg_winning_points))
overall_home_wp
```


Plot 11a: Teamwise average points lost from winning positions
```{r}
ggplot(home_winning_points, mapping = aes(x=home_team, y = home_avg_winning_points, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Average Points lost from winning positions", title = " Teamwise average points lost from winning positions", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```


Plot 11b: Overall average points lost from winning positions
```{r}
ggplot(overall_home_wp, mapping = aes(x=fans_present, y = wp)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) + labs(x = "Fans Presence", y = "Overall points lost from losing positions", title = "Overall average points lost from winning positions", fill = "Presence of Fans")
```



```{r}
both_seasons$home_sot_perc = both_seasons$home_shots_on_target / both_seasons$home_shots * 100
both_seasons$away_sot_perc = both_seasons$away_shots_on_target / both_seasons$away_shots * 100

both_seasons
```


```{r}
home_sot_percentage = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_home_sot = mean(home_sot_perc))

away_sot_percentage = both_seasons %>%
                        group_by(home_team, fans_present) %>%
                        summarize(avg_away_sot = mean(away_sot_perc))

home_sot_percentage
away_sot_percentage
```

```{r}
overall_home_sot_perc = home_sot_percentage %>%
                          group_by(fans_present) %>%
                          summarize(overall_home_sot = mean(avg_home_sot))

overall_away_sot_perc = away_sot_percentage %>%
                          group_by(fans_present) %>%
                          summarize(overall_away_sot = mean(avg_away_sot))

overall_home_sot_perc
overall_away_sot_perc
```


Plot 12a: Home shots on Target Percentage
```{r}
ggplot(home_sot_percentage, mapping = aes(x=home_team, y = avg_home_sot, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge", ) + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) + labs(x = "Team Name", y = "Shots on target %", title = "Average Shots on Target % for Home Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))

```

Plot 12b: Away Shots on Target Percentage
```{r}
ggplot(away_sot_percentage, mapping = aes(x=home_team, y = avg_away_sot, fill = fans_present)) + geom_bar(stat = "identity", position = "dodge") + theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1))+ labs(x = "Team Name", y = "Shots on target %", title = "Average Shots on Target % for Away Teams", fill = "Presence of Fans")+ scale_fill_discrete(name = "Fans Present", labels = c("No", "Yes"))
```

Plot 12c: Overall home shots on Target Percentage
```{r}
ggplot(overall_home_sot_perc, mapping = aes(x=fans_present, y = overall_home_sot)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"), width = 0.30) + labs(x = "Fans Presence", y = "Overall shots on target %", title = "Overall home shots on Target Percentage", fill = "Presence of Fans")
```

Plot 12d: Overall away shots on Target Percentage
```{r}
ggplot(overall_away_sot_perc, mapping = aes(x=fans_present, y = overall_away_sot)) + geom_bar(stat = "identity", fill = c("#ff6961", "#78c5dc"),width = 0.30) +  labs(x = "Fans Presence", y = "Overall shots on target %", title = "Overall Away shots on Target Percentage", fill = "Presence of Fans")
```

```{r}
write.csv(both_seasons, "both_seasons.csv")
```

```{r}
with_ht = both_seasons %>%
            filter(fans_present == 'Y')

wo_ht = both_seasons %>%
          filter(fans_present == 'N')

write.csv(with_ht, "with_ht.csv")
write.csv(wo_ht, "wo_ht.csv")
```

